---
title: "R Notebook"
output: html_notebook
---
# Hipotese 2

We think that, for a mixed workload with multiple short bursts processes and some
heavy processes, the scheduling algorithms that prioritize short processes will
be much more responsive.

To measure responsiveness we will use the average of ready_wait_time/burst.

To create this workload we created two workloads with the following parameters:
TODO: tabela
## long_solo
num_procs = 5
mean_io_bursts = 5
mean_iat = 10
min_CPU = 10
max_CPU = 20
min_IO = 10
max_IO = 20
## short_burst
num_procs = 100
mean_io_bursts = 100
mean_iat = 10
min_CPU = 0.1
max_CPU = 1
min_IO = 1
max_IO = 2

We then merged the two workloads by time of arrival of each process.

We generated 120 different seeds, 30 for each scheduler, to ensure that the samples are independent.

To test this we will first use an One-Way ANOVA test, defined as follows:
dependent variable : AVG(SCHEDULER(ready_wait_time/burst))
independent variable: scheduler
levels: FCFS, RR, SJF, SRTF

H0 : Ufcfs = Urr = ...
H1 : Existe 1 diferente


## Preparação dos dados
Quick insight of the workload
```{r}
source("utils.R")
wk_name = "mixed_h2_240"
pr = load_proc(wk_name)
ggplot(pr,aes(cpu_time,io_time)) + geom_hex()
ggplot(pr,aes(cpu_per_burst,cpu_time)) + geom_hex()
ggplot(pr,aes(cpu_per_burst,nbursts)) + geom_hex()
ggplot(pr,aes(cpu_time,nbursts)) + geom_hex()
```
## Example input for one seed

```{r}
wk = load_workload(wk_name)
wk %>%
  select(scheduler, ready_wait_time, rw_per_nbursts) %>%
  group_by(scheduler) %>%
  summarise_all(mean)
```

## Run OneWay ANOVA
```{r}
wk = load_workload(wk_name,all_seeds = TRUE)
wk = wk %>%
  select(scheduler,seed, rw_per_nbursts) %>%
  group_by(seed,scheduler) %>%
  summarise_all(mean)
print(wk)
step = 60
fcfs = filter(wk,scheduler == "FCFS" & seed <= step)
sjf  = filter(wk,scheduler == "SJF" & seed > step & seed <= 2*step)
rr   = filter(wk,scheduler == "RR" & seed > 2*step & seed <= 3*step)
srtf = filter(wk,scheduler == "SRTF" & seed > 3*step & seed <= 4*step)

wk = rbind(fcfs,sjf,rr,srtf)
boxplot(rw_per_nbursts ~ scheduler, wk)
```

TODO: explain outliers

```{r}
aov.out = aov(rw_per_nbursts ~ scheduler, data=wk)
summary(aov.out)
```
Lets check the assumptions:

```{r}
ggqqplot(aov.out$res)
shapiro.test(aov.out$res)
bartlett.test(rw_per_nbursts ~ scheduler, data = wk)
```

As neither of the assumptions was met, we cannot take conclusions from the one way ANOVA test. We will use the non-parametric Kruskal-Wallis rank sum test:
```{r}
kruskal.test(rw_per_nbursts ~ scheduler, data=wk)
```

As the p-value is < 0.05, we reject the null hypotesys. Post-hoc analysis can be 
done with dunn's test

```{r}
library(dunn.test)
dunn.test(wk$rw_per_nbursts,g=wk$scheduler,method="bonferroni")
```
From these tests we conclude that there are significant differences
between:
  FCFS and all others schedulers: ~
  RR is not unlike SRTF and SJF (at a 0.05 significance level)

```{r}
ggplot(wk, aes(rw_per_nbursts, color=scheduler)) + geom_density()
ggplot(wk, aes(rw_per_nbursts, color=scheduler)) + geom_boxplot()
```

