---
title: "R Notebook"
output: html_notebook
---

# Hipotese 3

One common benchmark is the cpu utilization. To measure it we used 
$$ usage = \frac{cpu\_time}{max(arrival\_time+turnaround)}$$

We believe that SRTF will have an overall higher CPU usage because it will dispatch
more processes to the io queue. On the other hand, schedulers like FCFS will take longer,
having less cpu usage, because the processes will accumulate in the ready wait queue while
the io queue is empty.

To test this hypothesis we will use a paired T-test.

Formaly, we have:
$$
H_0 = usage(SRTF) = usage(FCFS)\\
H_1 = usage(SRTF) > usage(FCFS)
$$

Quick insight of the workload
```{r}
source("utils.R")
wk_name = "h3"
pr = load_proc(wk_name)
ggplot(pr,aes(cpu_time,io_time)) + geom_hex()
ggplot(pr,aes(cpu_per_burst,cpu_time)) + geom_hex()
ggplot(pr,aes(cpu_per_burst,nbursts)) + geom_hex()
ggplot(pr,aes(cpu_time,nbursts)) + geom_hex()
```


Data preparation

```{r}
wk = load_workload(wk_name,all_seeds = TRUE)
wk = calc_usage(wk)
```
Even tough our n>30, we will still check normality (in the case that we change our data in the future)

```{r}
fcfs = wk[wk$scheduler=="FCFS",]
srtf = wk[wk$scheduler=="SRTF",]

shapiro.test(fcfs$usage)
ggqqplot(fcfs$usage)

shapiro.test(srtf$usage)
ggqqplot(srtf$usage)
```

