---
title: "R Notebook"
output: html_notebook
---

# Hipotese 3

One common benchmark is the cpu utilization. To measure it we used 
$$ usage = \frac{cpu\_time}{max(arrival\_time+turnaround)}$$
We believe that, for a system with mixed short and long processes, SRTF will have an overall higher CPU usage because it will dispatch
more processes to the io queue. On the other hand, schedulers like FCFS will take longer to complete the workload,
having less cpu usage, because the processes will accumulate in the ready wait queue while the io queue is empty.

To test this hypothesis we will use a paired T-test.

Formaly, we have:
$$
H_0 = usage(SRTF) = usage(FCFS)\\
H_1 = usage(SRTF) > usage(FCFS)
$$

Quick insight of the workload
```{r}
source("utils.R")
wk_name = "h3"
pr = load_proc(wk_name)
ggplot(pr,aes(cpu_time,io_time)) + geom_hex()
ggplot(pr,aes(cpu_per_burst,cpu_time)) + geom_hex()
ggplot(pr,aes(cpu_per_burst,nbursts)) + geom_hex()
ggplot(pr,aes(cpu_time,nbursts)) + geom_hex()
```


Data preparation

```{r}
wk = load_workload(wk_name,all_seeds = TRUE)
wk = calc_usage(wk)
```
Even tough our n>30, we will still check normality (in the case that we change our data in the future)

```{r}
fcfs = wk[wk$scheduler=="FCFS",]
srtf = wk[wk$scheduler=="SRTF",]

shapiro.test(fcfs$usage)
ggqqplot(fcfs$usage)

shapiro.test(srtf$usage)
ggqqplot(srtf$usage)

```
The T-test yielded the following results:

```{r}
t.test(
  fcfs$usage, srtf$usage, paired = TRUE, alternative = "less"
)
```

As expected, the p-value is lower than our confidence level of 0.05, so we reject the null hypothesis, meaning 
the average of used cpu is significantly different between the FCFS and SRTF.

## Analysis
The workloads were formed by merging two runs of the generator script. Our idea was the following: schedulers that
switched contexts more often would offload more processes to the io queue. Ideally, both the cpu and the IO controller
would be working at the same time, but in a first come first served fashion the queue would build up on the cpu/io queue, depending
on which was slower. Following this logic we can broaden out hypothesis and reformulate it:
$$
H_0 = usage(SRTF) = usage(SJF) = usage(RR)\\
H_1 = \exists{i,j}: usage_i \neq usage_j
$$

Testing 

These conclusions become more apparent with the following visualization:

```{r}
ggplot(wk,aes(usage,color=scheduler)) + geom_density()
```


